%LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.1in  % start text higher on the page
% \setlength{\textheight}{10in} % increase text height to fit resume on 1 page

%\usepackage{fancyhdr}
%\pagestyle{fancy}
%\fancyhead{}
%\fancyfoot[R]{\thepage}

\usepackage{hyperref}


\pagestyle{plain}

\def\pvn{\textbf{Nguyen, P-H.V.}}

\begin{document}  
\name{\hspace{0.05in} Paul-Hieu V. Nguyen \\  \hspace{0.45in} March 2023}
                        
\begin{resume}                        
  
  \section{CONTACT} 
  1300 University Ave., 1250 Medical Sciences Center, Madison, WI 53706 \\
  Phone: 408-802-1105 \\ 
  Primary Email: pvnguyen5@wisc.edu \\
  % Secondary Email: sameerd@alum.mit.edu \\
  Website: \texttt{https://paulhnguyen.github.io}

  \section{RESEARCH INTERESTS}
  Bayesian hierarchical modeling. Bayesian treed regression. Model selection. 
              
% \section{EMPLOYMENT} 

% \textbf{University of Wisconsin--Madison}, Dept.~of Statistics \hfill Madison, WI \\
% \textit{Assistant Professor} \hfill August 2021 -- present

% \textbf{Massachusetts Institute of Technology}, CSAIL \hfill Cambridge, MA \\
% \emph{Postdoctoral Associate} \hfill September 2018 -- August 2021 \\
% Supervisor: Tamara Broderick
              
\section{EDUCATION}      
                {\bf University of Wisconsin--Madison} \hfill Madision, WI \\
                Ph.D., Statistics \hfill August 2022 - Present \\
		% Thesis Title: ``Bayesian model selection and estimation without MCMC'' \\
		% Thesis Supervisors: Ed George and Veronika Ro\v{c}kov\'{a}
                
                {\bf Reed College} \hfill Portland, OR \\
                B.A., Mathematics \hfill May 2022 \\
                Thesis Title: ``Inference for Random Forests'' \\
                Thesis Supervisor: Jonathan Wells, Ph.D.
  
  
% \section{PRE-PRINTS}


\section{PUBLICATIONS}

Wojcik O.C., Olson S.D., \pvn, McConville K.S., Moisen G.G. and Frescino T.S. (2022). ``GREGORY: A Modified Generalized Regression Estimator Approach to Estimating Forest Attributes in the Interior Western US.'' \textit{Frontiers in Forests and Global Change}. (accepted). \\ \href{https://doi.org/10.3389/ffgc.2021.763414}{DOI: 10.3389/ffgc.2021.763414}

%\section{WORKING PAPERS \& PAPERS IN PROGRESS}


\section{HONORS \& AWARDS} 

Advanced Opportunity Fellowship, University of Wisconsin--Madison \hfill Aug 2022

2nd, June 2020 Undergraduate Research Project Competition \hfill Sep 2020

2020 Economics Summer Research Mintz Award, Reed College \hfill Aug 2020

Commendation for Excellence, Reed College \hfill Aug 2019, 2020, 2021, 2022

\section{TEACHING}

\textbf{University of Wisconsin--Madison}

Stat 240: {\it Data Science Modeling I} \hfill Fall 2023

\textbf{Reed College} 

Math 392: {\it Mathematical Statistics} \hfill Spring 2022

Math 391: {\it Probability} \hfill Fall 2021

Math 243: {\it Statistical Learning} \hfill Fall 2020

Math 141: {\it Introduction to Probability and Statistics} \hfill Fall 2019, Spring 2020, Spring 2021

% \section{DEPARTMENT \hspace{0.1in} SEMINARS}

\section{TALKS}

2021 Presentation. \pvn “Anonymity in the Ubuntu Dialogue Corpus.” Electronic Undergraduate Statistics Research Conference.

2021 Presentation. \pvn “Anonymity in the Ubuntu Dialogue Corpus.” Reed College Summer Research Poster Session.

2020 Presentation. Wojcik O.C., Olson S.D. and \pvn. “Improving Precision of Forestry Estimation.” Electronic Undergraduate Statistics Research Conference.

\section{EXPERIENCE}

\emph{NSF REU Fellow}, Pennsylvania State University \hfill Summer 2021 \\
Supervisor: Ting-Hao 'Kenneth' Huang, Ph.D.

\emph{Economics Summer Fellow}, Reed College \hfill Summer 2020 \\
Supervisor: Nicholas Wilson, Ph.D.

\emph{Research Assistant}, Reed College \hfill Spring 2020 \\
Supervisor: Kelly McConville, Ph.D.

\emph{Iowa Summer Institute in Biostatistics Fellow}, University of Iowa \hfill Summer 2019 \\
Supervisor: Grant Brown, Ph.D.

% \section{SERVICE}

\end{resume} 
\end{document}










%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
