%LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.1in  % start text higher on the page
% \setlength{\textheight}{10in} % increase text height to fit resume on 1 page

%\usepackage{fancyhdr}
%\pagestyle{fancy}
%\fancyhead{}
%\fancyfoot[R]{\thepage}

\usepackage{hyperref}


\pagestyle{plain}

\def\pvn{\textbf{Nguyen, P-H.V.}}

\begin{document}  
\name{\hspace{0.05in} Paul-Hieu V. Nguyen \\  \hspace{0.45in} Nov 2024}
                        
\begin{resume}                        
  
  \section{CONTACT} 
  1300 University Ave., 1250 Medical Sciences Center, Madison, WI 53706 \\
  Phone: 408-802-1105 \\ 
  Primary Email: pvnguyen5@wisc.edu \\
  % Secondary Email: sameerd@alum.mit.edu \\
  Website: \texttt{https://paulhnguyen.github.io}

  \section{RESEARCH INTERESTS}
  Tree Ensemble Methods. Bayesian tree regression. Bayesian Statistics. Model selection. Statistical Learning. Applications in environment.
              
% \section{EMPLOYMENT} 

% \textbf{University of Wisconsin--Madison}, Dept.~of Statistics \hfill Madison, WI \\
% \textit{Assistant Professor} \hfill August 2021 -- present

% \textbf{Massachusetts Institute of Technology}, CSAIL \hfill Cambridge, MA \\
% \emph{Postdoctoral Associate} \hfill September 2018 -- August 2021 \\
% Supervisor: Tamara Broderick
              
\section{EDUCATION}      
                {\bf University of Wisconsin--Madison} \hfill Madision, WI \\
                Ph.D., Statistics \hfill August 2022 - Present \\
		% Thesis Title: ``Bayesian model selection and estimation without MCMC'' \\
		% Thesis Supervisors: Ed George and Veronika Ro\v{c}kov\'{a}
                
                {\bf Reed College} \hfill Portland, OR \\
                B.A., Mathematics \hfill May 2022 \\
                Thesis Title: ``Inference for Random Forests'' \\
                Thesis Supervisor: Jonathan Wells, Ph.D.
  
  
% \section{PRE-PRINTS}


\section{PUBLICATIONS}

Wojcik O.C., Olson S.D., \pvn, McConville K.S., Moisen G.G. and Frescino T.S. (2022). ``GREGORY: A Modified Generalized Regression Estimator Approach to Estimating Forest Attributes in the Interior Western US.'' \textit{Frontiers in Forests and Global Change}. \\ \href{https://doi.org/10.3389/ffgc.2021.763414}{DOI: 10.3389/ffgc.2021.763414}

\section{WORKING PAPERS}

\pvn, Yee. R, Deshpande, S.K.. (2024+). ``Oblique Bayesian additive regression trees''. \href{https://arxiv.org/abs/2411.08849}{arXiv:2411.08849}.

\section{TALKS}

Presentation. \pvn ``Oblique BART''. Joint Statistical Meetings (2024).

Presentation. \pvn ``Oblique Bayesian Additive Regression Trees with non-axis aligned splits''. Midwest Machine Learning Symposium (2024).

Poster Presentation. \pvn ``Oblique Bayesian Additive Regression Trees''. Midwest Machine Learning Symposium (2024).

Presentation. Yee R., \pvn  ``Extensions to BART: Oblique Rules and Random Fourier Features". Institute for the Foundations of Data Science (2024).

Presentation. \pvn ``Anonymity in the Ubuntu Dialogue Corpus.” Electronic Undergraduate Statistics Research Conference (2021).

Poster Presentation. \pvn ``Anonymity in the Ubuntu Dialogue Corpus.” Reed College Summer Research Poster Session (2021).

Presentation. Wojcik O.C., Olson S.D. and \pvn ``Improving Precision of Forestry Estimation.” Electronic Undergraduate Statistics Research Conference (2020).

Presentation. Harris L., Richter M. and \pvn ``Modeling Lyme Disease in Iowa.” 10th Annual Iowa Summer Research Symposium (2019).


\section{HONORS \& AWARDS} 

Advanced Opportunity Fellowship, University of Wisconsin--Madison \hfill Aug 2022

2nd, June 2020 Undergraduate Research Project Competition \hfill Sep 2020

2020 Economics Summer Research Mintz Award, Reed College \hfill Aug 2020

Commendation for Excellence, Reed College \hfill Aug 2019, 2020, 2021, 2022

\section{TEACHING}

\textbf{University of Wisconsin--Madison}; Teaching Assistant

Stat 340: {\it Data Science Modeling II} \hfill Fall 2024

Stat 240: {\it Data Science Modeling I} \hfill Fall 2023, Spring 2024

\textbf{Reed College}; Teaching Assistant, Lab Assistant, Grader 

Math 392: {\it Mathematical Statistics} \hfill Spring 2022

Math 391: {\it Probability} \hfill Fall 2021

Math 243: {\it Statistical Learning} \hfill Fall 2020

Math 141: {\it Introduction to Probability and Statistics} \hfill Fall 2019, Spring 2020, Spring 2021

% \section{DEPARTMENT \hspace{0.1in} SEMINARS}

\section{EXPERIENCE}

\emph{Research Assistant}, University of Wisconsin -- Madison \hfill Summer 2024 \\
Supervisor: Sameer K. Deshpande, Ph.D.

\emph{NSF REU Fellow}, Pennsylvania State University \hfill Summer 2021 \\
Supervisor: Ting-Hao 'Kenneth' Huang, Ph.D.

\emph{Economics Summer Fellow}, Reed College \hfill Summer 2020 \\
Supervisor: Nicholas Wilson, Ph.D.

\emph{Research Assistant}, Reed College \hfill Spring 2020 \\
Supervisor: Kelly McConville, Ph.D.

\emph{Iowa Summer Institute in Biostatistics Fellow}, University of Iowa \hfill Summer 2019 \\
Supervisor: Grant Brown, Ph.D.

% \section{SERVICE}

\section{SKILLS}

\textbf{Programming}: R, C++, Python, Latex \\
\textbf{Software}: Stan, Git

\end{resume} 
\end{document}










%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
